The Actions We Compute are Not Invariant

### 2018-12-04 paper/ms.tex
Update paper

\subsection{Cluster Simulations} \label{ssec:cluster_sim} We simulate a small
star cluster of $256$ stars in the frozen $\z=0$ potential of
$\texttt{m12i}$.

We use the simple tree code
\texttt{pykdgrav}\footnote{\url{https://github.com/omgspace/pykdgrav},
commit:\texttt{fbd1ddc}}.

>>>>

\subsection{Cluster Simulations} \label{ssec:cluster_sim}
We simulate a small star cluster of $256$ stars in the frozen $\z=0$
potential of $\texttt{m12i}$. We use the code \texttt{ph4} within the
\texttt{AMUSE} framework \citep{2011ascl.soft07007P, 2013CoPhC.184..456P,
2013A&A...557A..84P} for the cluster integration. We use a softening length
of $0.01\,\pc$ which means we do not correctly solve the internal dynamics of
the cluster, but this is not important for our purposes. To couple the
gravitational forces of the frozen snapshot to the cluster stars, we use the
\texttt{BRIDGE} \citep{2007PASJ...59.1095F}, also implemented in
\texttt{AMUSE}. Our simulation runs for $2\,\Gyr$, allowing us to solve for
$\sim 10$ orbits.

To compute the forces from the frozen potential, we use the simple tree code
\texttt{pykdgrav}\footnote{\url{https://github.com/omgspace/pykdgrav},
commit:\texttt{fbd1ddc}}.
